Visualize Non-Euclidean Actors Social Media via Joint Social Relationship Representations, Network Characteristics and Media Sentiments

### 2020-10-13 A-BasicCommom/CVPR2021/cvpr_vision.tex
1.remove arXiv ref according to CVPR policy.

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, also named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media , social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of GRU layer in long sequences of film cast,
  the mapping ability of CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Shi \etal's model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
  as a result, it is 14\% higher in accuracy than Shi \etal ~\cite{shi2019c}'s model.

@@

  Shi \etal~\cite{shi2019c} proposed a C-LSTM classification model, using single-layer CNN for extracting the high-order dimensional representation of text,
  and connecting to LSTM layers for sentence representation, the trained neural network model has an accuracy of 87.8\%.

@@

Machine learning methods such as Linear Regression, SVN, MLP, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also has a significant impact on the box-office,
so the machine learning fitting process can't converge in a given time.
Using the Cartisticdecision tree regression algorithm to make box-office prediction for the test set film,
the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the Qiu and Tang~\cite{qiu2018microblog} model,
and the average absolute deviation of the model is $0.1285$ million, about 28.56\% of the average box-office.
The explanation of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models,
according to the prediction model structure schematic of movie box-office,
the characteristics can be sorted according to the importance, the social network structure characteristics are the most important,
the social network text sentiments characteristics, the film meta-data are important, and the social network characteristics are generally important.
Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and twitter index algorithm's 95.71\% determination of coefficient,
The Cartisticmodel in this paper has a determination of coefficient of 98.58\% which has a 2.87\% improvement.

@@

In summary, randomly choose 10 movies as a test set, as shown in Table 1.
The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
Compared to Zhou \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
Therefore, it can provide decision-making advice in the task of selecting suitable actors for to-be-cast film,
and in the box-office prediction task, the model can provide reasonable predictions in the market.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Zhou \etal  & 61.54\% \\
This paper & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on different model.}
\end{table}

@@

According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
I proposed an FC-GRU-CNN box-office prediction model, and tested on a dataset of $1296$ movies released in China mainland from 2011 to 2015, compared to Zhou \etal's model, accuracy improves 14\%.

>>>>

  In the film industry, visualizing actor stars' social media for analyzing audience intention towards movies is essential to movie producers.
  However, non-Euclidean social media is hard to analyze, I propose an FC-GRU-CNN architecture, also named as \underline{N}on-\underline{E}uclidean \underline{N}et, for social media visualization.
  On the analysis of social media , social relationship representations, network characteristics and media sentiments are key factors.
  FC-GRU-CNN architecture exploits the long-term memory ability of GRU layer in long sequences of film cast,
  the mapping ability of CNN layer in retrieving all-pairs shortest path feature of the actors' social relationship,
  and non-linear capability of deep FC layer for movie text sentiments and other characteristics.
  The proposed model accuracy is 14\% higher than Read \etal's model.

@@

  With the development of social networks, actors' influence of social media is increasing, and the influence of actors' consumption spreads through social networks,
  and using long-term social network data to study the relationships between all actors, directors, and films remains a challenge.
  It is easy to see that the relationship between box-office and the director, actors, scriptwriters, and producers are often non-linear, that is,
  it is difficult to use linear functions to build box-office prediction models.
  By analyzing the social network characteristics of movie actors, sentiments of movies in Sina Weibo posts, all-pairs shortest path,
  it is easy to get the priority of each characteristic by analysis of feature importance,
  the existing prediction algorithm only makes use of the film meta-data, lacks the study on the social network characteristics of the actors,
  though the traditional explanation of the film box-office prediction algorithm is sufficing, however, the prediction accuracy is not satisfactory.
  This paper presents a model, named FC-GRU-CNN, for movie box-office prediction, combining characteristics of film meta-data, actors' social network measurement,
  all-pairs shortest path, social network text sentiments, and actors' artisticcontribution characteristics,
  as a result, it is 14\% higher in accuracy than Read \etal ~\cite{read2016earning}'s model.

@@

  Read \etal ~\cite{read2016earning} proposed a CNN-RNN classification model, using CNN layers for extracting the high-order dimensional representation of images,
  and connecting to LSTM layers for description representation, the trained neural network model has accuracy of 56.8\% on Caltech-UCSD Birds dataset and accuracy of 65.6\% on Flowers dataset.

@@

Machine learning methods such as Linear Regression, SVN, MLP, Logistic Regression, and Na{\'i}ve Bayes cannot converge on the data set,
possibly because the sentiments on actors' social networks do not represent the commercial benefits of the film.
Actors, as creators of films, have a role to play in the box-office, but lack of other important features that also has a significant impact on the box-office,
so the machine learning fitting process can't converge in a given time.
Using the Cartisticdecision tree regression algorithm to make box-office prediction for the test set film,
the experimental results show that the prediction model has a determination coefficient of 96.05\% on the test set and 98.58\% on the training set, which is 2.87\% higher than the Qiu and Tang~\cite{qiu2018microblog} model,
and the average absolute deviation of the model is $0.1285$ million, about 28.56\% of the average box-office.
The explanation of the decision tree prediction model is more intuitive and more interpretable than linear regression, logical regression, deep neural network and other models,
according to the prediction model structure schematic of movie box-office,
the characteristics can be sorted according to the importance, the social network structure characteristics are the most important,
the social network text sentiments characteristics, the film meta-data are important, and the social network characteristics are generally important.
Compared to Qiu and Tang~\cite{qiu2018microblog}'s logistic regression model on sentiments and twitter index algorithm's 95.71\% determination of coefficient,
The model in this paper has a determination of coefficient of 98.58\% which has a 2.87\% improvement.

@@

In summary, randomly choose 10 movies as a test set, as shown in Table 1.
The accuracy of the binary classification model on the training set reached 99.61\%, the accuracy on the test set is 75\%.
Compared to Read \etal model, see Table 2, the proposed FC-GRU-CNN model converges on the training set and achieves better prediction results on the test set.
Therefore, it can provide decision-making advice in the task of selecting suitable actors for to-be-cast film,
and in the box-office prediction task, the model can provide reasonable predictions in the market.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Model & F1-score \\
\hline\hline
Read \etal  & 61.54\% \\
This paper & 75.0\% \\
\hline
\end{tabular}
\end{center}
\caption{Performance comparison on different model.}
\end{table}

@@

According to the NEN(Non-Euclidean Net) box-office prediction model, this paper discussed the relationship between the movie meta-data, Sina Weibo text sentiments, social relationship representations, network characteristics, and actors' artistic contribution in detail.
I proposed an FC-GRU-CNN box-office prediction model, and tested on a dataset of $1296$ movies released in China mainland from 2011 to 2015, compared to Read \etal's model, accuracy improves 14\%.
